\documentclass[12pt, a4paper]{article}

\usepackage[top=0.9in, bottom=0.8in, left=0.7in, right=0.8in]{geometry}
\usepackage{sectsty}
\usepackage{enumitem}
\usepackage{fancyhdr}
\usepackage{lastpage}
\usepackage{hyperref}
\usepackage[parfill]{parskip}
\usepackage{bm}

\renewcommand{\headrulewidth}{0pt}

\hypersetup{
    colorlinks=true,
    linkcolor=black,
    filecolor=black,      
    urlcolor=black,
    }
\usepackage[dvipsnames]{xcolor}

% set font style
\usepackage{helvet}
\usepackage[T1]{fontenc}

% set heading style
\usepackage{titlesec}
\titleformat{\section}{
  \vspace{-8pt}\bf\scshape\large\raggedright
}{}{0em}{}[\vspace{-6pt}]
% \titleformat{\section}{
%   \vspace{-4pt}\bfseries\large\raggedright\MakeUppercase
% }{}{1em}{}[\vspace{-5pt}]

% set spacing
\setlength{\parskip}{1em}
\renewcommand{\baselinestretch}{1.15}

% set heaer and footer
\pagestyle{fancy}
\fancyhf{}
\fancypagestyle{firstpage}{
  \lhead{\textcolor{gray}{Last Updated on \today}}
}
\cfoot{\footnotesize{Page \thepage \hspace{1pt} of \pageref{LastPage}}}



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%



%----------------------------------------------------------------------------------------
%	Information
%----------------------------------------------------------------------------------------
\thispagestyle{firstpage}

{\par \centering\MakeUppercase{\Large\bf Guang Cheng} \par}
\vspace*{-2mm}
\centering
\footnotesize{National University of Singapore, Institute of Operations Research and Analytics} \\
\footnotesize{\#04-01, Innovation 4.0, 3 Research Link, Singapore 117602} \\
\footnotesize{\href{mailto:gcheng@u.nus.edu}{gcheng@u.nus.edu}} $\ \diamond \ $ \footnotesize{\href{https://gcheng-nus.github.io}{https://gcheng-nus.github.io}}



{\small
%----------------------------------------------------------------------------------------
%	Education
%----------------------------------------------------------------------------------------

\section*{Education}
\vspace*{0.4em}
\hrule height 0.4pt
\begin{itemize}[leftmargin=20pt, itemsep=6pt, parsep=0.2pt, topsep=1pt]

	\item[]
	\textbf{National University of Singapore, Singapore} \hfill \textit{2020 -- Present} \\
	\textit{Ph.D. Student in Operations Research and Analytics} \\
	Advisor: Joel Goh

	\item[]
	\textbf{University of Science and Technology of China, China} \hfill \textit{2016 -- 2021} \\
	\textit{M.S. in Management Science and Engineering}
	% Advisors: Jingui Xie, Zhichao Zheng (external)

	\item[]
	\textbf{Jiangnan University, China} \hfill \textit{2012 -- 2016} \\
	\textit{B.A. in Industrial Engineering}

\end{itemize}



%----------------------------------------------------------------------------------------
%	 Research Interests
%----------------------------------------------------------------------------------------

\section*{Research Interests}
\vspace*{0.4em}
\hrule height 0.5pt
\begin{itemize}[leftmargin=36pt, itemsep=6pt, parsep=0.2pt, topsep=1pt]

	\item Medical Decision Making
	
	\item Healthcare Operations Management
	
	% \item Scheduling Systems

\end{itemize}



%----------------------------------------------------------------------------------------
%	Working Paper
%----------------------------------------------------------------------------------------

\section*{Working Paper}
\vspace*{0.4em}
\hrule height 0.5pt
\begin{enumerate}[leftmargin=36pt, itemsep=6pt, parsep=0.2pt, topsep=1pt]

	\item Guang Cheng, Jingui Xie, Zhichao Zheng, Haidong Luo, Oon-Cheong Ooi.
	Extubation decision making with predictive information for mechanically ventilated patients in ICU.
	Major revision at {\it Management Science}.

\end{enumerate}



%----------------------------------------------------------------------------------------
%	Published Paper
%----------------------------------------------------------------------------------------

\section*{Published Papers}
\vspace*{0.4em}
\hrule height 0.5pt
\begin{enumerate}[leftmargin=36pt, itemsep=6pt, parsep=0.2pt, topsep=1pt]

	\item Guang Cheng, Sarah Yini Gao, Yancheng Yuan, Chenxiao Zhang, Zhichao Zheng. 
	On the test accuracy and effective control of the COVID-19 pandemic: A case study in Singapore. 
	{\it INFORMS Journal on Applied Analytics}, forthcoming.

	\item Jingui Xie, Guang Cheng, Zhichao Zheng, Haidong Luo, Oon-Cheong Ooi. 
	To extubate or not to extubate: Risk factors for extubation failure and deterioration with further mechanical ventilation. 
	{\it Journal of Cardiac Surgery}, 2019, 34(10): 1004–1011. 

\end{enumerate}



%----------------------------------------------------------------------------------------
%	Presentations
%----------------------------------------------------------------------------------------

\section*{Conference Presentations}
\vspace*{0.4em}
\hrule height 0.5pt
\begin{itemize}[leftmargin=36pt, itemsep=6pt, parsep=0.2pt, topsep=1pt]

	\item Extubation decision making with predictive information for mechanically ventilated patients in ICU

	\begin{itemize}[leftmargin=20pt, itemsep=2pt, topsep=2pt]

		\item {\it The 13th International Conference of CSAMSE}, virtual \hfill July 2021

		\item {\it POMS-HK International Conference}, Hong Kong, China \hfill January 2019
		
		\item {\it POMS Annual Conference}, virtual \hfill April 2022

	\end{itemize}

	\item The Impact of Introducing Release Policy for Operating Rooms on Surgery Waiting Times

	\begin{itemize}[leftmargin=20pt, itemsep=2pt, topsep=2pt]
		
		\item {\it IARS Annual Meeting}, poster presentation, virtual \hfill March 2022

		\item {\it POMS Annual Conference}, virtual \hfill April 2022

		\item {\it INFORMS Annual Meeting} (scheduled) \hfill October 2022
	
	\end{itemize}

\end{itemize}



%----------------------------------------------------------------------------------------
%	 Experience
%----------------------------------------------------------------------------------------

\section*{Professional Experience}
\vspace*{0.4em}
\hrule height 0.5pt
\begin{itemize}[leftmargin=36pt, itemsep=0pt, parsep=0.2pt, topsep=1pt]

	\item {\it Research Assistant}: Singapore Management University, Jul. 2019 -- Jun. 2020

	\item {\it Research Assistant}: Singapore Management University, Aug. 2018 -- Nov. 2018

  \item {\it Research Assistant}: Singapore Management University, Sep. 2017 -- Mar. 2018

\end{itemize}



%----------------------------------------------------------------------------------------
%	 Service
%----------------------------------------------------------------------------------------

\section*{Professional Service}
\vspace*{0.4em}
\hrule height 0.5pt
\begin{itemize}[leftmargin=36pt, itemsep=2pt, parsep=0pt, topsep=1pt]
	
	\item Session Chair, POMS Annual Conference \hfill April 2022

	\item Organizing Committee Member, Analytics for X Conference 2021 \hfill July 2021

\end{itemize}



%----------------------------------------------------------------------------------------
%	 Teaching
%----------------------------------------------------------------------------------------

\section*{Teaching Experience}
\vspace*{0.4em}
\hrule height 0.5pt
\raggedright\textbf{Teaching Assistant}
\begin{itemize}[leftmargin=36pt, itemsep=2pt, parsep=0pt, topsep=-0.5em]

	\item IE4214 Revenue Management and Pricing Analytics (Undergraduate) \hfill Spring 2022

\end{itemize}



%----------------------------------------------------------------------------------------
%	Honors
%----------------------------------------------------------------------------------------

\section*{Honors and Awards}
\vspace*{0.4em}
\hrule height 0.5pt
\begin{itemize}[leftmargin=36pt, itemsep=1pt, parsep=0.5pt, topsep=1pt]

	\item NUS Research Scholarship, National University of Singapore, Singapore, 2020
	
	% \item JData Data Mining Competition Top 10, JD.com, inc., China, 2017

	% \item National Scholarship, Ministry of Education of People’s Republic of China, China, 2015

	% \item Municipal Merit Student, Education Bureau of Wuxi, China, 2015

\end{itemize}



%----------------------------------------------------------------------------------------
%	Skills
%----------------------------------------------------------------------------------------

\section*{Skills}
\vspace*{0.4em}
\hrule height 0.5pt
\begin{itemize}[leftmargin=36pt, itemsep=2pt, parsep=0.2pt, topsep=1pt]

	\item {\it Programming \& Packages}: Python, R, MATLAB, SQL, Gurobi

\end{itemize}
}


% \vspace*{\fill}
% \center Last Updated on \today

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\end{document}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%